---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# IntegrativeHTE

The goal of *IntegrativeHET* is to 
implement integrative analyses for the heterogenous treatment effect
combining a randomized trial and a real-world evidence study.

Two datasets

* The randomized trial contains observations on (A,X,Y), where the treatment assignment A is randomized. 

* The real-world evidence study contains observations on (A,X,Y), where the treatment assignment A may be confounded.


## Installation with `devtools`:

```{r, eval = FALSE}
devtools::install_github("shuyang1987/IntegrativeHTE")
```

### Main Paper: coming soon

The reference paper will come soon.


### Usage

IntHTE(A, X, Y, delta, family.oc, gamma1=0.90, gamma2=2, nptb=50, nboots=50, alpha.CI=0.05)

### Arguments

Argument  | 
------------- | -------------
A	|is a vector of treatment  ( (n+m) x 1), where n is the RT sample size and m is the RW sample size
X	| is a matrix of covariates without intercept  ( (n+m) x p)
Y |	is a vector of outcome  ( (n+m) x 1)
delta |is a vector of the binary indicator of belonging to the randomized trial (RT) sample; i.e., 1 if the unit belongs to the RT sample, and 0 otherwise  ( (n+m) x 1)
family.oc	|specifies the family for the outcome model
-- |"gaussian": a linear regression model for the continuous outcome
-- |"binomial": a logistic regression model for the binary outcome
nptb |is the number for replication-based method for estimating Sigma_SS
gamma1|	is the parameter in the violation test such that T > chisq_{1-gamma1} indicates the bias of the RW analysis is significant
gamma2|is a smooth parameter in using the normal cummulative distribution with mean 0 and variance gamma2^2 function to approximate the indicator function
nboots|	is the number of bootstrap samples
alpha.CI| is the level of percentile bootstrap confidence interval


### Value

 | 
------------- | -------------
est | the HTE estimators including
i)  |  the covariate adjustment estimator;
ii) |  the RT estimating equation estimator;
iii)| the RT&RW estimating equation estimator;
iv) |  the elastic integrative estimator.
ve|   the bootstrap variance estimate for est. Note: ve is conservative for the elastic integrative estimator.
boot.CI|  1-alpha.CI percentiel bootstrap confidence interval for the elastic integrative estimator


## Example

This is an example for illustration.

```{r example}

set.seed(1234)

library(MASS)
library(rootSolve)
library(stats)
library(utils)
library(IntegrativeHTE)

n <- 1e5
beta0<- c(0,1,1)
psi0 <- c(1,1,1)

family.oc <- "binomial" #family.oc <- "gaussian"

X.pop <- cbind(rnorm(n,0,1),rnorm(n,0,1))
if( family.oc=="gaussian" ){
  Y0   <-  cbind(1,X.pop)%*%beta0+rnorm(n,0,1)
  Y1   <-  cbind(1,X.pop)%*%beta0+cbind(1,X)%*%psi0+rnorm(n,0,1)
}
if( family.oc=="binomial" ){
  lY0   <- -cbind(1,X.pop)%*%psi0
  lY1   <-  cbind(1,X.pop)%*%psi0
  pY0 <- exp(lY0)/(1+exp(lY0) )
  pY1 <- exp(lY1)/(1+exp(lY1) )
  Y0    <- rbinom(n,1, pY0 )
  Y1    <- rbinom(n,1, pY1 )
}

## RCT data
eS <- expoit(-cbind(1,X.pop)%*%c(5.5,1,1))
S <- sapply(eS,rbinom,n = 1, size = 1)
S.ind <- which(S==1)
n.t <- length(S.ind)
X.t <- X.pop[S.ind,]
Y0.t <- Y0[S.ind]
Y1.t <- Y1[S.ind]
A.t  <- rbinom(n.t,1,0.5) # randomly assign treatment to trial participant
Y.t  <-  Y1.t*A.t+Y0.t*(1-A.t)

## OS data
m <- 5000
P.ind <- sample(1:n,size = m)
X.os <- X.pop[P.ind,]
Y0.os <- Y0[P.ind]
Y1.os <- Y1[P.ind]

eA <- expoit( cbind(1,X.os)%*%c(1,-1,-1))

A.os <- sapply(eA,rbinom,n=1,size=1)
Y.os <- Y1.os*A.os+Y0.os*(1-A.os)

A<-c(A.t,A.os)
X<-rbind(X.t,X.os)
Y<-c(Y.t,Y.os)
delta<-c(rep(1,n.t),rep(0,m))

IntegrativeHTE::IntHTE(A, X, Y, delta, family.oc, gamma1=0.90, gamma2=2, nptb=50, nboots=50, alpha.CI=0.05)


```
